---
title: "TzeFungLung_Assign7"
author: "jim lung"
date: "10-12-2017"
output: html_document
---

# Data605 Assignment 7

## 1. Let X1 , X2, . . . , Xn be n mutually independent random variables, each of which is uniformly distributed on the integers from 1 to k. Let Y denote the minimum of the Xi¡¦s. Find the distribution of Y .

The uniformly distributed on the integers from 1 to k, the miniumum value of Y is one Xi from Xi's:

Assume the distribution function P(Y=z) = min{X1,X2,X3....Xi}

Case 1:
Assumption:
Y=1, which is minimum sample Xi
(Select one sample from 10 samples)
x = {1,2,3,4,5}
Size of all sample x = {1,2,3,4,5} : $5^{10}$
Size of non-sample x = {1,2,3,4} : $(5-1)^{10}$
$P(Y=1)= ((5-0)^{10}-(5-1)^{10} )/ 5 ^{10}$

Case 2:
Assumption:
(Select 2 sample from 10 samples)
x = {1,2,3,4,5}
Size of all sample: $5^{10}$
Size of non-sample = $(5^{10}-4^{10})+3^{10}$
$P(Y=1)= (5^{10}-(5^{10}-4^{10})-3^{10})/ 5 ^{10}$

Using avariables:
\[k^{n} - (k^{n} - (k-1)^{n}) - (k-2)^{n} \]
\[= (k-1)^{n}-(k-2)^{n} \]

When m=2;
\[=((k+m-1)^{n} - (k-m)^{n})/k^{n} \]


## 2. Your organization owns a copier (future lawyers, etc.) or MRI (future doctors). This machine has a manufacturer¡¦s expected lifetime of 1 0 years. This means that we expect one failure every ten years. (Include the probability statements and R Code for each part.)

### a. What is the probability that the machine will fail after 8 years?. Provide also the expected value and standard deviation. Model as a geometric. (Hint: the probability is equivalent to not failing during the first 8 years..)

Using geometric distribution: $p(X=n) = (1-p)^{n-1}*p$
P(failure) = 1/10 =0.1
P(Success) = 0.9

\[P(X < 9)= 0.1+0.1*0.9+0.1*0.9^{2}+....+0.1*0.9^{7} =0.6125 \]

\[P(X\geqslant 9)= 1-0.6125 = 0.3874\]

```{r}
1-pgeom(8,0.1)
```

### b. What is the probability that the machine will fail after 8 years?. Provide also the expected value and standard deviation. Model as an exponential.

Exponential density: 

$\mu = 10$

$\lambda = \frac{1}{\mu}$

$\lambda = 0.1$

\[P(T \leq 8) = 1-e^{-0.1*8} = 0.5506\]

\[P(T > 8) = 1-0.5506 = 0.4493\]
```{r}
1-pexp(8,0.1)

```

#### Expected value
$\lambda = 0.1$
```{r}
Exp <- 1/0.1
Exp
```

#### Standard deviation
$\lambda = 0.1$
```{r}
var <- 1/(0.1^2)
sd <- sqrt(var)
sd
```

### c. What is the probability that the machine will fail after 8 years?. Provide also the expected value and standard deviation. Model as a binomial. (Hint: 0 success in 8 years)

p=0.1  and q=0.9

\[P(X \leq 8) = 0.1^00.9^8 = 0.9^8 = 0.4304\]
```{r}
pbinom(0,8,0.1)
```

Expected value:
```{r}
n=8
p=0.1
Exp1 <- n*p
Exp1
```

Standard Deviation:
```{r}
q=0.9
var1 <- n*p*q
sd1 <- sqrt(var1)
sd1
```

### d. What is the probability that the machine will fail after 8 years?. Provide also the expected value and standard deviation. Model as a Poisson.

```{r}
n <- 8        
p <- 1 / 10 
#lambda
ld <- n * p

# success
x <- 0

p0 <- ((ld^x * ((exp(1))^(-1*ld)))/factorial(x))
p0

```

```{r}
ppois(0, ld)
```

Expected value:
$E[X] =\lambda = 0.8$

Standard Deviation:
```{r}

var2 <- ld
sd2 <- sqrt(var2)
sd2
```



