---
title: "TzeFungLung_Assign2"
author: "jim lung"
date: "09-07-2017"
output: html_document
---

# Problem 1

__1. Show that $A^T A \neq AA^T$ in general. (Proof and demonstration.)__

\[Assume A=\begin{bmatrix} 2 & 3\\ 2 & 4 \end{bmatrix}\]
\[A^{T}=\begin{bmatrix} 2 & 2\\ 3 & 4 \end{bmatrix}\]
\[A^{T}A=\begin{bmatrix} 2 & 2\\ 3 & 4 \end{bmatrix}\begin{bmatrix} 2 & 3\\ 2 & 4 \end{bmatrix} = \begin{bmatrix} 8 & 14\\ 14 & 25 \end{bmatrix}\]
\[AA^{T}=\begin{bmatrix} 2 & 3\\ 2 & 4 \end{bmatrix}\begin{bmatrix} 2 & 2\\ 3 & 4 \end{bmatrix} = \begin{bmatrix} 13 & 16\\ 16 & 20 \end{bmatrix}\]

From the above result, it is prove that $A^T A \neq AA^T$

__2. For a special type of square matrix A, we get $A^T A = AA^T$ . Under what conditions could this be true? (Hint: The Identity matrix I is an example of such a matrix).__

A matrix is symmetric $A^T A = AA^T$ if it equals its own transpose, for example: \[\begin{bmatrix} 1 & 3 & 4\\ 3 & 7 & 8\\ 4& 8 & 5 \end{bmatrix}\] is symmetric.

```{r}

A <- matrix(c(1,3,4,3,7,8,4,8,5), 3)
A
S <- t(A) %*% A
S
M <- A %*% t(A)
M

```


# Problem 2

Matrix factorization is a very important problem. There are supercomputers built just to do matrix factorizations. Every second you are on an airplane, matrices are being factorized. Radars that track flights use a technique called Kalman filtering. At the heart of Kalman Filtering is a Matrix Factorization operation. Kalman Filters are solving linear systems of equations when they track your flight using radars.

Write an R function to factorize a square matrix A into LU or LDU, whichever you prefer. You don't have to worry about permuting rows of A and you can assume that A is less than 5x5, if you need to hard-code any variables in your code. 

##Fuction to factorize a square matrix into LDU:

```{r}
factorization <- function(A){
  if (nrow(A) == ncol(A)){
    U <- A
    L <- diag(nrow(A))
    
    
    for(i in 1:(nrow(A)-1)){
      for(j in (i+1):nrow(A)){
        L[j,i] <- U[j,i]/U[i,i]
        U[j,] <- U[j,]-U[i,]*L[j,i]
      }
    }
    
     D <- diag(nrow(A))
    
    for(k in 1:nrow(A)){
     
      D[k,k] <- U[k,k]
      U[k,] <- U[k,]/D[k,k]
      
    }
    
  } else {
    NM <- "Matrix is not square."
    NM
  }
list("A" = A, "L" = L, "D" = D, "U" = U) 
  
}


```

## Testing the fuction:

$$A = \left[ \begin{array}{cc}1 & 1 & 2 \\2 & 1 & 0 \\3 & 1 & 1 \end{array} \right]$$
```{r}
A <- matrix(c(1, 2, 3, 1, 1, 1, 2, 0, 1), 3,3)

factorization(A)
```

$$A = LDU' = \left[ \begin{array}{cc}1 & 0 & 0 \\2 & 1 & 0 \\3 & 2 & 1 \end{array} \right] \left[ \begin{array}{cc}1 & 0 & 0 \\0 & -1 & 0 \\0 & 0 & 3 \end{array} \right] \left[ \begin{array}{cc}1 & 1 & 2 \\0 & 1 & 4 \\0 & 0 & 1 \end{array} \right]$$



