---
title: "TzeFungLung_Assign3"
author: "jim lung"
date: "09-15-2017"
output: html_document
---

#Problem Set 1
##1. What is the rank of the matrix $A$?
$$ A = \begin{bmatrix}1 & 2 & 3 & 4 \\-1 & 0 & 1 & 3 \\0 & 1 & -2 & 1 \\5 & 4 & -2 & -3\end{bmatrix}$$ 
$$ A = \begin{bmatrix}1 & 2 & 3 & 4 \\0 & 2 & 4 & 7 \\0 & 1 & -2 & 1 \\5 & 4 & -2 & -3\end{bmatrix} (R2 <- R1 +R2)$$
$$ A = \begin{bmatrix}1 & 2 & 3 & 4 \\0 & 2 & 4 & 7 \\0 & 1 & -2 & 1 \\0 & -6 & -17 & -23\end{bmatrix} (R4 <- -5R1 +R4)$$

$$ A = \begin{bmatrix}1 & 2 & 3 & 4 \\0 & 2 & 4 & 7 \\0 & 1 & -2 & 1 \\0 & 0 & -5 & -2\end{bmatrix} (R4 <- 3R2+R4)$$
$$ A = \begin{bmatrix}1 & 2 & 3 & 4 \\0 & 2 & 4 & 7 \\0 & 0 & -4 & -5/2 \\0 & 0 & -5 & -2\end{bmatrix} (R3 <- 1/2R2+R3)$$
$$ A = \begin{bmatrix}1 & 2 & 3 & 4 \\0 & 2 & 4 & 7 \\0 & 0 & -4 & -5/2 \\0 & 0 & 0 & 9/8\end{bmatrix} (R4 <- 5/4R2+R4)$$

$$ Rank\,\,=\,4 $$
### R solution
```{r}
library(matrixcalc)

m <- matrix(c(1,2,3,4,-1,0,1,3,0,1,-2,1,5,4,-2,-3), nrow = 4, ncol = 4, byrow = TRUE)
m
matrix.rank(m)
```
   
##2. Given an $mxn$ matrix where $m>n$, what can be the maximum rank? The minimum rank, assuming that the matrix is non-zero?   
    
The Maximum rank is $m$ (rows)    
The Minimum rank is 1, the others rows may be linearly dependent.  
     
##3. What is the rank of matrix $B$?
$$ B = \begin{bmatrix}1 & 2 & 1 \\3 & 6 & 3 \\2 & 4 & 2 \end{bmatrix}$$    

$$ B = \begin{bmatrix}1 & 2 & 1 \\0 & 0 & 0 \\2 & 4 & 2 \end{bmatrix} (R2 <- -3R1+R2)$$ 
$$ B = \begin{bmatrix}1 & 2 & 1 \\0 & 0 & 0 \\0 & 0 & 0 \end{bmatrix} (R3 <- -2R1+R3)$$ 
$$ Rank\,\,=\,1 $$   
R2 and R3 are linearly dependent.
```{r}
# Test
m <- matrix(c(1,2,1,3,6,3,2,4,2), nrow = 3, ncol = 3, byrow = TRUE)
m
matrix.rank(m)
```
   
#Problem Set 2
Compute the eigenvalues and eigenvectors of the matrix A. You¡¦ll need to write out the characteristic polynomial and show your solution.   
Eigenvalues:

##characteristic polynomial:
$$ P(\lambda)=det(A-\lambda\,I_n)=0$$ 
$$ A = \begin{bmatrix}1 & 2 & 3 \\0 & 4 & 5 \\0 & 0 & 6 \end{bmatrix};\,\, \lambda\,I_3 = \begin{bmatrix}\lambda & 0 & 0 \\0 & \lambda & 0 \\0 & 0 & \lambda \end{bmatrix}$$ 

$$ det\,\begin{bmatrix}1-\lambda & 2 & 3 \\0 & 4-\lambda & 5 \\0 & 0 & 6-\lambda \end{bmatrix} = 0$$ 
$$(1-\lambda)(4-\lambda)(6-\lambda)=0$$
$$ \lambda ^{3}-11\lambda^{2}+34\lambda-24=0$$
##Eigenvalues of A:
$$\lambda=1,\, \lambda=4,\, \lambda=6$$
   
##Eigenvectors:   


#### $\lambda_1=6$

$$(A- \lambda_1I)v=0$$

$$-5x + 2y + 3z = 0 \\ -2y + 5z = 0$$
If we make $$Y=1$$:
$$-2 + 5z = 0; z = 2/5$$
Substituting Y and Z:
$$-5x + 2 + 3(2/5) = 0 \\ -5x = -16/5 \\ x = 16/25$$
$$E_{\lambda_1=6}=c\begin{bmatrix}16/25 \\ 1 \\ 2/5\end{bmatrix}$$

#### $\lambda_2=4$

$$(A- \lambda_2 I)v=0$$

$$-3x + 2y + z = 0\\ 5z = 0\\2z = 0$$
If we set $$Y=1$$ then $$X=2/3$$
$$E_{\lambda_2=4}=c\begin{bmatrix}2/3 \\ 1 \\ 0\end{bmatrix}$$

#### $\lambda_3=1$

$$(A- \lambda_3 I)v=0$$

$$\begin{bmatrix}0&2&3\\0&3&5\\0&0&5\end{bmatrix}\begin{bmatrix}X\\Y\\Z\end{bmatrix}=0$$

Equations:  
$$2y + 3z = 0\\ 3y + 5z = 0\\5z = 0$$

The only non-zero solution is $$X=1$$ and Y and Z = 0
$$E_{\lambda_3=1}=c\begin{bmatrix}1 \\ 0 \\ 0\end{bmatrix}$$


### Test

```{r}
library(pracma)
mat <- matrix(data = c(1,0,0,2,4,0,3,5,6), nrow = 3, ncol = 3, byrow = FALSE)
mat
charpoly(mat)
eigen(mat)

# eign vectors
eigen(mat)$values
```


```{r}

#for L = 6
eigen(mat)$vectors[,1]

#for L = 4
eigen(mat)$vectors[,2]

#for L = 1
eigen(mat)$vectors[,3]
```