---
title: "TzeFungLung_Assign10"
author: "jim lung"
date: "11-03-2017"
output: html_document
---

# Data 605 Assignment 10

## Smith is in jail and has 1 dollar; he can get out on bail if he has 8 dollars. A guard agrees to make a series of bets with him. If Smith bets A dollars, he wins A dollars with probability .4 and loses A dollars with probability .6. Find the probability that he wins 8 dollars before losing all of his money if

### (a) he bets 1 dollar each time (timid strategy).


```{r}
p <- 0.4
q <- 0.6
r <- q/p


for (i in 0:8){
P <- round((1-r^i)/(1-r^8),4)
print (P)
}
```

P(1) is 0.0203

### (b) he bets, each time, as much as possible but not more than necessary to bring his fortune up to 8 dollars (bold strategy).

```{r}
b <- matrix(c(1,0.6,0.6,0.6,0,0,0,0,0,0,0,0.4,0,0,0,0,0,0.4,0,0,0,0,0,0.4,1),nrow = 5, byrow=FALSE)
b
b1 <- matrix(c(0,1,0,0,0),nrow=1)
b1
b2 <- b1 %*% b
b2
b3 <- b2 %*% b
b4 <- b3 %*% b
b4
```
The probability is 0.064

### (c) Which strategy gives Smith the better chance of getting out of jail?
The probability of bold strategy is better than timid strategy to get out of jail.
