---
title: "TzeFungLung_Assign7"
author: "jim lung"
date: "10-12-2017"
output: html_document
---

# Data605 Assignment 7

## 1. Let X1 , X2, . . . , Xn be n mutually independent random variables, each of which is uniformly distributed on the integers from 1 to k. Let Y denote the minimum of the Xi¡¦s. Find the distribution of Y .

The uniformly distributed on the integers from 1 to k, the miniumum value of Y is one Xi from Xi's:

Assume the distribution function P(Y=z) = min{X1,X2,X3....Xi}

Case 1:
Assumption:
Y=1, which is minimum sample Xi
(Select one sample from 10 samples)
x = {1,2,3,4,5}
Size of all sample x = {1,2,3,4,5} : \[5^{10}\]
Size of non-sample x = {1,2,3,4} : \[(5-1)^{10}\]
\[P(Y=1)= ((5-0)^{10}-(5-1)^{10} )/ 5 ^{10}\]

Case 2:
Assumption:
(Select 2 sample from 10 samples)
x = {1,2,3,4,5}
Size of all sample: \[5^{10}\]
Size of non-sample = \[(5^{10}-4^{10})+3^{10}\]
\[P(Y=1)= (5^{10}-(5^{10}-4^{10})-3^{10})/ 5 ^{10}\]

Using avariables:
\[k^{n}???(k^{n}???(k???1)^{n})???(k???2)^{n}\]
\[=(k???1)^{n}???(k???2)^{n}\]

When m=2;
\[=((k+m-1)^{n}???(k???m)^{n})/k^n\]


## 2. Your organization owns a copier (future lawyers, etc.) or MRI (future doctors). This machine has a manufacturer¡¦s expected lifetime of 1 0 years. This means that we expect one failure every ten years. (Include the probability statements and R Code for each part.)

### a. What is the probability that the machine will fail after 8 years?. Provide also the expected value and standard deviation. Model as a geometric. (Hint: the probability is equivalent to not failing during the first 8 years..)

```{r}


```

### b. What is the probability that the machine will fail after 8 years?. Provide also the expected value and standard deviation. Model as an exponential.

```{r}


```

### c. What is the probability that the machine will fail after 8 years?. Provide also the expected value and standard deviation. Model as a binomial. (Hint: 0 success in 8 years)



### d. What is the probability that the machine will fail after 8 years?. Provide also the expected value and standard deviation. Model as a Poisson.





