---
title: "TzeFungLung_Assign4"
author: "jim lung"
date: "09-20-2017"
output: html_document
---
#Data605 Assignment4
#Problem Set 1

Given a 3 ¡Ñ 3 matrix: 
$$A = \begin{bmatrix}-1 & 1 & 5 \\1 & 3 & 0 \\0 & -2 & 1\end{bmatrix}$$
Write code in R to compute $X = AA^T$ and $Y = A^TA$. Then, compute the eigenvalues and eigenvectors of X and Y using the built-in commands in R.
   
```{r}
# matrix
A = matrix(c(-1,1,0,1,3,-2,5,0,1), 3, 3)
A
# Compute X and Y:

x <- A%*%t(A)
x
y <- t(A)%*%A
y

# compute eigenvalues and eigenvectors
eigen_x <- eigen(x)
eigen_x
eigen_y <- eigen(y)
eigen_y
```
Now, compute the left-singular, singular values, and right-singular vectors of A using the `svd()` command. 
```{r}
svd_A <- svd(A)
svd_A # v = right, u = left
```
Examine the two sets of singular vectors and show that they are indeed eigenvectors of X and Y.
```{r}
# Compare left singular vector u to the eigenvectors of x
eigen_x$vectors
svd_A$u
round(abs(eigen_x$vectors)) == round(abs(svd_A$u))
```
Vectors are same except one of the vectors multiplied by a scalar of -1, it is just a scalar on the same plane. Left singular vectors are the eigenvectors of X. it perform with the eigenvectors of Y and the right singular vectors.
```{r}
(eigen_y$vectors)
(svd_A$v)
round(abs(eigen_y$vectors)) == round(abs(svd_A$v))
```
Non-zero eigenvalues of both X and Y are the same and are squares of the non-zero singular values of A.   
```{r}
# all.equal
all.equal(eigen_x$values, (svd_A$d)^2)
all.equal(eigen_y$values, (svd_A$d)^2)
```

#Problem Set 2
Write a function to compute the inverse of a well-conditioned full-rank square matrix using co-factors. You may use built-in R commands to compute the determinant. Your function should have the following signature: `B = myinverse(A)` where `A` is a matrix and `B` is its inverse and $A¡ÑB = I$.    

A matrix is full rank if all rows and columns are linearly independent.   
```{r}
inverse <- function(A) {

  #Check invertible
  if (det(A) == 0) {
    stop('matrix is non-invertible')
  }
  
  m <- nrow(A)
  n <- ncol(A)
  
  # create co-factor matrix
  co_m <- diag(0, nrow=m, ncol=n)
  
  #compute the cofactors
  
  #and calculate the det() and sign
  for(i in 1:m)
  {
    for(j in 1:n)
    {
        co_m[i,j] <- (-1)^(i+j)*det(A[-i,-j]) # calculate by minior
    }
  } 
  co_m
  
  #Inverse of A = t(co_m)/det(A) -- t() gives transpose
  return((t(co_m) / det(A)))
}

# Try it out 
A = matrix(c(1,9,18,1,2,3,-5,-4,3), 3, 3)
A
B <- inverse(A)
B

# Check using solve() -- for inverse of square matrix
s_A <- solve(A)
round(s_A,2) == round(B,2)
```

