---
title: "TzeFungLung_Assign11"
author: "jim lung"
date: "11-09-2017"
output: html_document
---

# Data 605 Assignment 11

## Using the ¡§cars¡¨ dataset in R, build a linear model for stopping distance as a function of speed and replicate the analysis of your textbook chapter 3 (visualization, quality evaluation of the model, and residual analysis.)


```{r}
# cars data
head(cars)
```

```{r}
summary(cars)
```

## visualization

```{r}
carslm <- lm(cars$dist ~ cars$speed)
plot(cars$speed, cars$dist, main = "Comparsion between speed and distance", xlab = "speed", ylab="distance")
abline(carslm)
```

## Linear Regression Model

```{r}
# correlation
cor(cars$dist,cars$speed)
```
It is a strong uphill (positive) linear relationship.


```{r}
# linear regression model
carslm <- lm(cars$dist ~ cars$speed)
summary(carslm)
```

When Y is stop distance and X is spreed, the linear model is as follow:
$Y = -17.5791 + 3.9324 X$

It is a a statistically significant predictor of evaluation score with p-value less than 0.05.
For Multiple R-squared, the model is around 65% fits the data.

```{r}
# histogram of residuals
hist(carslm$residuals)
```

Histogram of residual plot appear to be near normally distributed.

```{r}
# qqplot
qqnorm(carslm$residuals)
qqline(carslm$residuals)
```

Q-Q plot are not uniformly scattered and have deviation at lower and quantiles. The residuals does not show randomly.


